---
title: "Readme-rmarkdown"
author: "Frank"
date: "2020/8/8"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
```

# rgantt 

![](http://www.r-pkg.org/badges/version/rgantt)

This package is to create a gantt chart(bar chart that illustrates a project schedule) with desired data.frame.

This package can create an interactive gantt chart in R. It is a wrapper of Javascript library [Frappe Gantt](https://github.com/frappe/gantt)

## Installation

Dev version (Not on CRAN yet)

``` r
devtools::install_github("frankzhangsyd/rgantt") 
```

## Introduction

Simply create a data frame with `id` `start` `end` `name` `progress` `dependecies` columns.
Then pass this data frame into `rgantt()` function.

```{r}
df <- data.frame(
  stringsAsFactors = FALSE,
                id = c("Task 0","Task 1","Task 2",
                       "Task 3","Task 4","Task 5","Task 6"),
             start = c("2020-08-07","2020-08-08",
                       "2020-08-08","2020-08-10","2020-08-14","2020-08-15",
                       "2020-08-17"),
               end = c("2020-08-14","2020-08-11",
                       "2020-08-11","2020-08-13","2020-08-14","2020-08-16",
                       "2020-08-17"),
              name = c("Redesign website",
                       "Write new content","Upgrade systeme","Apply new styles","Review",
                       "Deploy","Go Live!"),
          progress = c(37L, 75L, 75L, 23L, 21L, 61L, 32L),
      dependencies = c(NA,"Task 0","Task 0",
                       "Task 1, Task 2","Task 3",NA,"Task 5")
)
```

The easiest way to start is copying code above and modify your version!

```{r results="show"}
knitr::kable(df)
```

```{r}
library(rgantt)
rgantt(df)
```

